---
title: "Homework 8"
author: "Anna Moeller"
date: "April 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(boot)
library(Sleuth3)
```

# Problem 2
```{r}
# Mean salamanders per plot
mn <- function(d, i) mean(d$Salamanders[i])
b_mn <- boot(case2202, mn, 1e5)
boot.ci(b_mn)
plot(b_mn)

# Correlation between forest age and salamanders
correl <- function(d, i) cor(d$ForestAge[i], d$Salamanders[i])
b_correl <- boot(case2202, correl, 1e5)
boot.ci(b_correl)
plot(b_correl)

```
For both analyses, the plots look approximately normal, and the percentile and normal confidence intervals are similar. Therefore, the distribution is approximately normal, and I would use the normal confidence interval. 

# Problem 3
```{r}

# Function to calculate coverage for one confidence interval
cover_fn <- function(x, n, truth){
  m <- mean(x)
  sig_prime <- sd(x)
  c <- qt(0.975, n - 1)
  d <- c * sig_prime/sqrt(n)
  LCI <- m - d
  UCI <- m + d
  cover <- LCI <= truth & truth <= UCI
  return(cover)
}

# Calculate coverage for nsim CIs with under one n
coverage_wrapper_one_n <- function(X, n, truth){
  cover <- purrr::map_lgl(X, ~cover_fn(.x, n, truth) )
  # Coverage
  coverage <- mean(cover)
  return(coverage)
}
norm_one_n <- function(nsim, n, true_mu) {
  X <- purrr::rerun(nsim, rnorm(n, true_mu, 2)) 
  coverage_wrapper_one_n(X, n, true_mu)
}
t_one_n <- function(nsim, n, truth) {
  X <- purrr::rerun(nsim, rt(n, 3))
  coverage_wrapper_one_n(X, n, truth)
}
exp_one_n <- function(nsim, n, truth) {
  X <- purrr::rerun(nsim, rexp(n, 1))
  coverage_wrapper_one_n(X, n, truth)
}

# Run over multiple n
nsim <- 100000
n <- c(10, 25, 100)
```
Normal distribution
```{r}
purrr::map_dbl(n, ~norm_one_n(nsim, .x, true_mu = 5))
```

T-distribution
```{r}
purrr::map_dbl(n, ~t_one_n(nsim, .x, truth = 0))
```

Exponential distribution
```{r}
purrr::map_dbl(n, ~exp_one_n(nsim, .x, truth = 1))
```

Confidence interval coverage was accurate for both the normal and t-distributions for all n. 
For the exponential distribution, coverage was accurage with larger n (n = 100). 

# Problem 4
```{r}
# write a new cover_fn for variance
cover_fn <- function(x, n, truth){
  c1 <- qchisq(.05/2, df = n-1)
  c2 <- qchisq(1-.05/2, df = n-1)
  xbar <- mean(x)
  top <- sum((x - xbar)^2)
  LCI <- top/c2
  UCI <- top/c1
  # Coverage for this CI
  cover <- LCI <= truth & truth <= UCI
  return(cover)
}

# Only need to rewrite normal because others don't depend on parameter to simulate
norm_one_n <- function(nsim, n, true_var) {
  X <- purrr::rerun(nsim, rnorm(n, 1, sqrt(true_var)) )
  coverage_wrapper_one_n(X, n, true_var)
}

# Run over multiple n

```
Normal distribution
```{r}
purrr::map_dbl(n, ~norm_one_n(nsim, .x, true_var = 5))
```

T-distribution
```{r}
purrr::map_dbl(n, ~t_one_n(nsim, .x, truth = 3))
```

Exponential distribution
```{r}
purrr::map_dbl(n, ~exp_one_n(nsim, .x, truth = 1))
```

This confidence interval appears to be very sensitive to violations of normality. For non-normal distributions, coverage is very low at all sample sizes. 